Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-19 chi2012.tex
yes

For the first prestudy, we designed and ran a semi-structured interview to discover the processes and tools people would use when combining data from multiple websites. We interviewed 8 participants and asked them a range of questions regarding their use of multiple websites in gathering information. We then inquired as to how each participant would go about planning various aspects of a large party, such as date, location and entertainment.

>>>>

For the first prestudy, we conducted a semi-structured interview to understand the reasons and ways that people drew information from diverse information sources. We interviewed 8 participants, asking them to identify tasks that performed recently that required use of multiple information sources, the kinds of sources used, and the tools used to manage the resulting information.  We then inquired as to how each participant would go about planning various aspects of a large party, such as date, location and entertainment.
